Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-02-24 paper/pears.tex

@@

%% separation plots
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{separation_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs \remove{\st{closely resembles a power law distribution}} across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is $81(71)\,\kpc$, to $z=1$, where median separations are $171(124)\,\kpc$. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:sep}
\end{figure*}

>>>>

\kc{ to $z=1$, where median separations are $171(124)\,\kpc$}

\kc{ ,. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.}

@@

%% separation plots
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{separation_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The typical separation between major (minor) dwarf pairs increases from $42(38)\,\kpc$ at $z=4$ to a peak of $128(109)\,\kpc$ at $z=0$.
  % Massive Pairs
  The separation between major (minor) massive pairs, on the other hand, increases from $81(71)\,\kpc$ at $z=4$ to $288(205)\,\kpc$ at  $z=0$.
  % Difference plots
  (Bottom) The median difference and 1-99\% range of the difference between major and minor pairs from 1000.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:sep}
\end{figure*}
